### 2017-10-25 pkg/model4you/inst/JORS/man_model4you.Rnw
comments Achim
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@1665 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 41aa96587e88cdda1f89cc2bd0161efd6d33a9d3

\paragraph{(1) Model-based trees} identify subgroups where within the subgroups
the model parameters are similar and between groups the model parameters are
different. This is achieved by finding instabilities in the model parameters
with respect to a variable (characteristicum) and recursively partitioning the
data into groups. If, for example the algorithm finds that men and women have
differing treatment effects, the data is partitioned into two subgroups.
Details on model-based trees in general can be found in
\citep{zeileis_model-based_2008} and for the special use case for stratified
treatment effect estimation in \citep{seibold_model-based_2016}.  Just a single
line of code lets the user compute a model-based tree in R:
<<eval=FALSE>>=
strat_models <- pmtree(base_model)
@
Note that \Sexpr{'pmtree()'} uses the data given in the call of the base 
model. It automatically uses variables not used in the model formula 
(in the example above \Sexpr{'response ~ treatment'}) as potential subgroup 
defining variables. This can be edited using the \Sexpr{'zformula'} argument.

\paragraph{(2) Personalised models} use model-based random forests to estimate
similarity of individuals in terms of model parameters. For each individual a
personalised model can be estimated based on a weighted set of the original
data, where the similarity measure corresponds to the weight. Details on the
personalised models can be found in \citep{seibold_individual_2017}.  
Computing personalised models for all observations in the training data is
simple:
<<eval=FALSE>>=
pm_forest <- pmforest(base_model)
pers_models <- pmodel(pm_forest)
@ 
Again here the potential effect-modifying variables are taken by default
as all variable not given in the model formula and can be defined using 
the \Sexpr{'zformula'} argument in \Sexpr{'pmforest()'}.

% \begin{figure}
% \centering
% \include{pmworkflow}
% \caption{Personalised models workflow: from real world to interpretable
% visualisation.}
% \end{figure}

@@

\begin{description}[noitemsep,topsep=0pt]
\item[Name:] CRAN
\item[Persistent identifier:] \url{https://cran.r-project.org/web/packages/model4you/index.html} %TODO upload to CRAN
\item[Licence:] GPL-2
\item[Publisher:] Heidi Seibold 
\item[Version published:] \textcolor{blue}{The version number of the software archived.}
\item[Date published:] \textcolor{blue}{dd/mm/yy}
\end{description}

@@

\begin{description}[noitemsep,topsep=0pt]
\item[Name:] R-forge
\item[Persistent identifier:] \url{https://r-forge.r-project.org/projects/partykit/}
\item[Licence:] GPL-2
\item[Date published:] \textcolor{blue}{dd/mm/yy} %TODO
\end{description}

@@

\section*{Competing interests}

The authors declare that they have no competing interests.

>>>>

\paragraph{1. Model-based trees} identify subgroups where within the subgroups
the model parameters are similar and between groups the model parameters are
different. This is achieved by finding instabilities in the model parameters
with respect to a variable (characteristicum) and recursively partitioning the
data into groups. If, for example the algorithm finds that men and women have
differing treatment effects, the data is partitioned into two subgroups.
Details on model-based trees in general can be found in
\citep{zeileis_model-based_2008} and for the special use case for stratified
treatment effect estimation in \citep{seibold_model-based_2016}.  Just a single
line of code lets the user compute a model-based tree in R:
<<eval=FALSE>>=
strat_models <- pmtree(base_model)
@
Note that \Sexpr{'pmtree()'} uses the data given in the call of the base 
model. It automatically uses variables not used in the model formula 
(in the example above \Sexpr{'response ~ treatment'}) as potential subgroup 
defining variables. This can be edited using the \Sexpr{'zformula'} argument.

\paragraph{2. Personalised models} use model-based random forests to estimate
similarity of individuals in terms of model parameters. For each individual a
personalised model can be estimated based on a weighted set of the original
data, where the similarity measure corresponds to the weight. Details on the
personalised models can be found in \citep{seibold_individual_2017}.  
Computing personalised models for all observations in the training data is
simple:
<<eval=FALSE>>=
pm_forest <- pmforest(base_model)
pers_models <- pmodel(pm_forest)
@ 
Again here the potential effect-modifying variables are taken by default
as all variable not given in the model formula and can be defined using 
the \Sexpr{'zformula'} argument in \Sexpr{'pmforest()'}.

@@

\begin{description}[noitemsep,topsep=0pt]
\item[Name:] CRAN
\item[Persistent identifier:] \url{https://cran.r-project.org/package=model4you} %TODO upload to CRAN
\item[Licence:] GPL-2 | GPL-3
\item[Publisher:] Heidi Seibold 
\item[Version published:] \textcolor{blue}{The version number of the software archived.}
\item[Date published:] \textcolor{blue}{dd/mm/yy}
\end{description}

@@

\begin{description}[noitemsep,topsep=0pt]
\item[Name:] R-forge
\item[Persistent identifier:] \url{https://r-forge.r-project.org/projects/partykit/}
\item[Licence:] GPL-2 | GPL-3
\item[Date published:] \textcolor{blue}{dd/mm/yy} %TODO
\end{description}

@@

\section*{Competing interests}
The authors declare that they have no competing interests.
